Modelling Weddell Sea Food Web

### 2022-01-27 ModellingWeddellSea.Rmd
De donde vienen los parametros alometricos?
Origen de parametros alometricos
added some thougths to draft.md ModellingWeddellSea.Rmd

# Parameters for alometric equations
#
n0 <- -1.16 
g <- -0.75

>>>>

# Parameters for alometric equations @Emmerson2004 y ... 
# @Yang2019 --> Parametriza Lotka Volterra
# @Donohue2017 --> Parametriza model derived from Yodzis and Innes (1992), updated with more recent allometric coefficients
# @Fahimipour2014 ---> Estima el flujo a partir de la tasa metabólica y las densidad de la poblacion
# @Carrara2015  --> distintos metodos para estimar interacciones basados en LV
#
# @Petchey2008 LV Parametrization an interesting idea is that it adds Type 2 functional response to check structural robustness 
#
# @Brose2006 Parametrization of consumer–resource model (Yodzis & Innes 1992) updated with new allometric coefficients (Brown et al. 2004)
# and extended to multispecies systems (Williams & Martinez 2004b)
#
# @James2015 Uses @Emerson2004 as a method to get LV interaction strength using body masses 
#
# @Neutel2014 Uses LV parametrized from empirical data 
# @Pawar2012 ------------------------------------------------- YES

n0 <- -1.16 
g <- -0.75
